Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-10-31 Paper.Rmd
formatting done

---
documentclass: report
title: 'Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?'
bibliography: references.bib
csl: apa.csl
link-citations: yes
output:
  bookdown::pdf_document2:
    fig.caption: yes
    includes:
      in_header: [non-float-fig.tex, custom.tex]
    toc_depth: 4
geometry: left=40mm, right=20mm, top=30mm, bottom=30mm
fontsize: 12pt
papersize: A4
linestretch: 1.25
fontfamily: times
---

@@

# Introduction

>>>>

---
documentclass: report
title: 'Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?'
bibliography: references.bib
csl: apa.csl
link-citations: yes
output:
  bookdown::pdf_document2:
    fig.caption: yes
    includes:
      in_header: [non-float-fig.tex, custom.tex]
    toc_depth: 4
geometry: left=40mm, right=20mm, top=30mm, bottom=30mm
fontsize: 12pt
papersize: A4
linestretch: 1.5
fontfamily: times
---

@@

# Introduction {-}
